Carrier phase and amplitude estimation for phase shift keying using pilots and data (Appendix)

### 2012-08-18 paper2.tex
added to papers

Here we compile lemmas required for the proof almost sure convergence (Theorem~\ref{thm:consistency}) and asymptotic normality (Theorem~\ref{thm:normality}) from the paper~\cite{McKilliam_leastsqPSKpilotsdata_2012}.  This document is not self contained and it is intended that the reader start at~\cite{McKilliam_leastsqPSKpilotsdata_2012} and refer to this document when prompted in~\cite{McKilliam_leastsqPSKpilotsdata_2012}.  The equation reference numbers in this document start at (\arabic{lasteqplusone}).  All equation numbers less than (\arabic{lasteqplusone}) refer back to~\cite{McKilliam_leastsqPSKpilotsdata_2012}.  The section numbers in this document start at~\arabic{lastsecplusone} and all sections before~\arabic{lastsecplusone} are contain in~\cite{McKilliam_leastsqPSKpilotsdata_2012}.  This document is separated into 3 sections.  Section~\ref{sec:proof-almost-sureappendix} contains those lemmas required for the proof of almost sure convergence (Theorem~\ref{thm:consistency}).  Section~\ref{sec:proof-asympt-normappendix} contains those lemmas required for the proof of asymptotic normality (Theorem~\ref{thm:normality}).  Section~\ref{sec:an-empirical-process} contains proofs for lemmas that arise in Section~\ref{sec:proof-asympt-normappendix}.  These involve the proof of~\emph{tightness} for certain empirical processes~\cite{Billingsley1999_convergence_of_probability_measures,Dudley_unif_central_lim_th_1999,Shorak_emp_proc_stat_2009}.

@@

\begin{lemma}\label{lem:chaining2}
There exists a positive constant $K_1$ such that
\[
\expect_{R,\Phi} \sup_{\sabs{\lambda} < \epsilon} \abs{ X(\lambda) } \leq K_1 \sqrt{C_\epsilon}.
\]
where $C_\epsilon$ is defined in~\eqref{eq:Cepsdefn}
\end{lemma}
\begin{IEEEproof}
Let $B_\epsilon = \{x \in \reals \mid \abs{x} < \epsilon\}$ be the set of real numbers with magnitude less than $\epsilon$.  For each non negative integer $k$, let $T_\epsilon(k)$ be a discrete subset of $B_\epsilon$ with the property that for every $\lambda \in B_\epsilon$ there exists $\lambda_1$ and $\lambda_2$ in $T_\epsilon(k)$ such that the psuedometric
\[
d_1(\lambda, \lambda_1) = \sum_{i \in P \cup D} \big( f_{i}(\lambda) - f_{i}(\lambda_1) \big)^2 \leq 2^{-k} C_\epsilon L,
\]
and the psuedometric
\[
d_2(\lambda, \lambda_2) = \sum_{i \in P \cup D} \sabs{f_{i}(\lambda) - f_{i}(\lambda_2)} \leq 2^{-k} D_\epsilon L
\]
where 
\begin{equation}\label{eq:Depsdefn}
D_\epsilon = \frac{1}{L}\epsilon\sum_{i\in P \cup D}R_i + \frac{1}{L}\sum_{i\in P \cup D}R_i I_{\epsilon}(\Phi_i).
\end{equation}
We specifically define $T_\epsilon(0)$ to contain only zero.  Defined this way, $T_\epsilon(0)$ satisfies the inequality above because $d_1(\lambda, 0) \leq C_\epsilon L $ and $d_2(\lambda, 0) \leq D_\epsilon L$ for all $\lambda \in B_\epsilon$, as a result of Lemma~\ref{lem:epslmlemma}.  The existance of $T_\epsilon(k)$ for every positive integer $k$ will be proved by construction in Lemma~\ref{lem:metricentropy}.  Lemma~\ref{lem:metricentropy} also shows that the number of elements in $T_\epsilon(k)$ is no more that $K_3 2^k$ where $K_3$ is a constant, independent of $L$, $\epsilon$ and $k$.

@@

\begin{lemma}\label{lem:epslmlemma}
Both $d_1(\lambda, 0) \leq C_\epsilon L $ and $d_2(\lambda, 0) \leq D_\epsilon L$ for all $\lambda \in B_\epsilon$.
\end{lemma}
\begin{IEEEproof}
We prove the lemma for $d_2$.  The proof for $d_1$ is similar.  Observe that $d_2(\lambda, 0) = c_1 + c_2$ where 
 \[
 c_1 = \sum_{i \in P} R_i\sabs{\sin(\lambda + \Phi_i) - \sin(\Phi_i) }
 \]
 and 
 \[
 c_2 = \sum_{i \in D} R_i \sabs{\sin\fracpart{\lambda + \Phi_i} - \sin\fracpart{\Phi_i}}.
 \]
 As $\sin(\cdot)$ is Lipshitz continuous with constant $K=1$,
 \[
 \sabs{\sin(\lambda + \Phi_i) - \sin(\Phi_i)} \leq K\sabs{\lambda} = \sabs{\lambda} < \epsilon
 \]
 for all $i \in P \cup D$, and therefore $c_1 \leq \epsilon \sum_{i \in P} R_i$.  Let $S = \{ i \in D \mid I_\epsilon(\Phi_i) = 1\}$. Now $c_2 = c_3 + c_4$ where 
 \[
 c_3 = \sum_{i \in D, i \in S} R_i \sabs{\sin\fracpart{\lambda + \Phi_i} - \sin\fracpart{\Phi_i}}
 \]
 and
 \[
 c_4 =  \sum_{i \in D, i \notin S} R_i \sabs{\sin\fracpart{\lambda + \Phi_i} - \sin\fracpart{\Phi_i}}.
 \]
 If $i \notin S$ then $\round{\lambda + \Phi_i} = \round{\Phi_i}$ for all $\sabs{\lambda} < \epsilon$ and therefore
 \begin{align*}
 \vert\sin&\fracpart{\lambda + \Phi_i} - \sin\fracpart{\Phi_i}\vert \\
 &= \sabs{\sin(\lambda + \Phi_i - \round{\Phi_i}) - \sin(\Phi_i - \round{\Phi_i})} \\
 &\leq \sabs{\lambda} < \epsilon
 \end{align*}
and so, 
\[
c_4 \leq \epsilon \sum_{i \in D, i \notin S} R_i \leq \epsilon \sum_{i \in D} R_i.
\]
Otherwise, if $i \in S$, then $\sabs{\sin\fracpart{\lambda + \Phi_i} - \sin\fracpart{\Phi_i}} \leq 2$ because $\sin(\cdot) \leq 1$.  Thus 
\[
c_3 \leq 2 \sum_{i \in D, i \in C} R_i \leq 2 \sum_{i \in D} R_i I_\epsilon(\Phi_i).
\]
Now
\begin{align*}
d_2(\lambda, 0) &= c_1 + c_2 \\
&\leq c_1 + c_3 + c_4 \\
&\leq \epsilon \sum_{i \in P \cup D} R_i + 2 \sum_{i \in D} R_i I_\epsilon(\Phi_i)
\end{align*}
as required
\end{IEEEproof}

\begin{lemma}\label{lem:limexpTk} With $T_\epsilon(k)$ defined as in Lemma~\ref{lem:chaining2},
\[
\lim_{k\rightarrow\infty}\expect_{R,\Phi}\sup_{\lambda \in T_\epsilon(k)} \sabs{X(\lambda)} = \expect_{R,\Phi} \sup_{\sabs{\lambda} < \epsilon} \sabs{X(\lambda)}
\]
\end{lemma}
\begin{IEEEproof}
Let $b_2(\lambda)$ be a function that maps $\lambda \in B_\epsilon$ to a point in $T_\epsilon(k)$ such that  $d_2(\lambda,b_2(\lambda)) \leq 2^{-k}D_\epsilon L$.  The existance of $b_2$ is guaranteed by the definition of $T_\epsilon(k-1)$.  So, for all $\lambda \in B_\epsilon$,
\begin{align*}
\sabs{X(\lambda) - X(b_2(\lambda))} &= \abs{\frac{1}{\sqrt{L}}\sum_{i\in P \cup D}g_i(f_i(\lambda) - f_i(b_2(\lambda)))} \\
&\leq  \frac{1}{\sqrt{L}}\sum_{i\in P \cup D}\abs{g_i}\sabs{f_i(\lambda) - f_i(b_2(\lambda))} \\
&\leq \frac{g_\text{max}}{\sqrt{L}} \sum_{i\in P \cup D}\sabs{f_i(\lambda) - f_i(b_2(\lambda))} \\
&\leq \frac{g_\text{max}}{\sqrt{L}} d_2(\lambda,b_2(\lambda)) \\
&\leq \frac{g_\text{max}}{\sqrt{L}} 2^{-k} D_\epsilon L,
\end{align*}
where $g_\text{max} = \max_{i\in P\cup D} \abs{g_i}$. The bound applies uniformly over $\lambda \in B_\epsilon$, so
\[
\sup_{\sabs{\lambda} < \epsilon} \sabs{X(\lambda) - X(b_2(\lambda))} \leq \frac{g_\text{max}}{\sqrt{L}} 2^{-k} D_\epsilon L.
\]
Applying $\expect_{R,\Phi}$ to both sides of this inequality,
\[
\expect_{R,\Phi} \sup_{\sabs{\lambda} < \epsilon} \sabs{X(\lambda) - X(b_2(\lambda))} \leq K_4 2^{-k} D_\epsilon L,
\]
where, as a result of Lemma~\ref{lem:maxineq},
\[
K_4 = \tfrac{1}{\sqrt{L}}\expect_{R,\Phi} g_\text{max} \leq 3 \sqrt{\frac{\log L}{L}}
\]
is a constant, independent of $\epsilon$ and $k$.  Because $T_\epsilon(k)$ is a subset of $B_\epsilon$,
\[
\sup_{\lambda \in T_\epsilon(k)} \expect_{R,\Phi} \sabs{X(\lambda)} \leq \sup_{\sabs{\lambda} < \epsilon} \expect_{R,\Phi} \sabs{X(\lambda)},
\]
and so,
\begin{align}
0 &\leq \sup_{\sabs{\lambda} < \epsilon} \expect_{R,\Phi} \sabs{X(\lambda)} - \sup_{\lambda \in T_\epsilon(k)} \expect_{R,\Phi} \sabs{X(\lambda)} \nonumber \\
&\leq \sup_{\sabs{\lambda} < \epsilon} \expect_{R,\Phi} \sabs{X(\lambda)} - \sup_{\sabs{\lambda} < \epsilon} \expect_{R,\Phi} \sabs{X(b_2(\lambda))} \nonumber \\
&\leq \sup_{\sabs{\lambda} < \epsilon} \expect_{R,\Phi} \big( \sabs{X(\lambda)} - \sabs{X(b_2(\lambda))} \big) \nonumber \\
&\leq \sup_{\sabs{\lambda} < \epsilon} \expect_{R,\Phi} \sabs{X(\lambda) - X(b_2(\lambda))} \nonumber \\
&\leq K_4 2^{-k} D_\epsilon L, \label{eq:Deps2nktozero}
\end{align}
the second line because,
\[
\sup_{\sabs{\lambda} < \epsilon} \expect_{R,\Phi} \sabs{X(b_2(\lambda))} \leq \sup_{\lambda \in T_\epsilon(k)} \expect_{R,\Phi} \sabs{X(\lambda)},
\]
since $b_2(\lambda) \in T_\epsilon(k)$.  The lemma follows from~\eqref{eq:Deps2nktozero} because $K_4 2^{-k} D_\epsilon L$ converges to zero as $k\rightarrow\infty$.
\end{IEEEproof}

@@

\begin{lemma}\label{lem:chaining3}(Chaining)
For all positive integers $k$,
\[
\expect_{R,\Phi} \sup_{\lambda \in T_\epsilon(k) } \abs{ X(\lambda) } \leq \sqrt{C_\epsilon} \sum_{i=1}^k \frac{5\sqrt{i \log 2 + \log K_3}}{2^{i/2}}.
\]
\end{lemma}
\begin{IEEEproof}
Let $b_1(\lambda)$ maps each $\lambda \in T_\epsilon(k)$ to an element in $T_\epsilon(k-1)$ such that $d(\lambda, b_1(\lambda)) \leq 2^{1-k}C_\epsilon L$.  The existance of $b_1$ is guaranteed by the definition of $T_\epsilon(k)$.  By the triangle inequality
\[
\sabs{X(\lambda)} \leq \sabs{X(b_2(\lambda))} + \sabs{X(\lambda) - X(b_2(\lambda))}  
\]
and taking supremums on both sides,
\begin{align}
&\sup_{\lambda \in T_\epsilon(k)}\sabs{X(\lambda)} \nonumber \\
&\leq \sup_{\lambda \in T_\epsilon(k)}\sabs{X(b_2(\lambda))} + \sup_{\lambda \in T_\epsilon(k)} \sabs{X(\lambda) - X(b_2(\lambda))}   \nonumber \\
&\leq \sup_{\lambda \in T_\epsilon(k-1)}\sabs{X(\lambda)} + \sup_{\lambda \in T_\epsilon(k)} \sabs{X(\lambda) - X(b_2(\lambda))}, \label{eq:Xb2recpreexp}
\end{align}
the last line because $b_2(\lambda) \in T_\epsilon(k-1)$ and so
\[
\sup_{\lambda \in T_\epsilon(k)}\sabs{X(b_2(\lambda))} \leq \sup_{\lambda \in T_\epsilon(k-1)}\sabs{X(\lambda)}.
\]
Conditional on $\{R_i\}$ and $\{\Phi_i\}$ the random variable
\[
U(\lambda) = X(\lambda) - X(b_2(\lambda))
\]
has zero mean, and it normally distributed with variance
\begin{align*}
\sigma_U^2 &= \expect_{R,\Phi} \frac{1}{L} \sum_{i \in P \cup D} g_i^2 \big( f_i(\lambda) - f_i(b_2(\lambda)) \big)^2 \\
&=  \frac{1}{L} \sum_{i \in P \cup D} \big( f_i(\lambda) - f_i(b_2(\lambda)) \big)^2 \\
&= d(\lambda, b_2(\lambda) \leq 2^{1-k} C_\epsilon,
\end{align*}
since $\expect_{R,\Phi}g_i^2 = 1$.  So, from Lemma~\ref{lem:maxineq},
\begin{align*}
\expect_{R,\Phi} \sup_{\lambda \in T_\epsilon(k)} \sabs{U(\lambda)} &\leq 3 \sqrt{ 2^{1-k} C_\epsilon \log \abs{T_\epsilon(k)} } \\
&\leq \sqrt{C_\epsilon} \frac{5\sqrt{k \log 2 + \log K_3}}{2^{k/2}}  
\end{align*}
Taking expectations on both sides of~\eqref{eq:Xb2recpreexp},
\begin{align*}
\expect_{R,\Phi}&\sup_{\lambda \in T_\epsilon(k)}\sabs{X(\lambda)} \\
&\leq \expect_{R,\Phi}\sup_{\lambda \in T_\epsilon(k-1)}\sabs{X(\lambda)} + \sqrt{C_\epsilon} \frac{5\sqrt{k \log 2 + \log K_3}}{2^{k/2}}  
\end{align*}
which involves a recursion in $k$.  By unravelling the recursion and using that $T_\epsilon(k)$ contains only zero, and therefore
\[
\expect_{R,\Phi} \sup_{\lambda \in T_k(0)} \sabs{X(\lambda)} = \expect_{R,\Phi} \sabs{X(0)} = 0
\]
we obtain,
\[
\expect_{R,\Phi}\sup_{\lambda \in T_\epsilon(k)}\sabs{X(\lambda)} \leq  \sqrt{C_\epsilon} \sum_{i=1}^k \frac{5\sqrt{i \log 2 + \log K_3}}{2^{i/2}}  
\]
as required.
\end{IEEEproof}

\begin{lemma}\label{lem:maxineq}(Maximal inequalities)
Suppose $X_1, \dots, X_N$ are $N$ zero mean Gaussian random variables each with variance less than some positive constant $K$.  Then
\[
\expect \sup_{n = 1, \dots, N} \abs{X_n} \leq 3  \sqrt{K \log N}
\]
where $\log N$ is the natural logarithm of $N$.
\end{lemma}
\begin{IEEEproof}
This result is well known, see for example~\cite[Section 3]{Pollard_asymp_empi_proc_1989}  
\end{IEEEproof}

>>>>

Here we compile lemmas required for the proof of almost sure convergence (Theorem~\ref{thm:consistency}) and asymptotic normality (Theorem~\ref{thm:normality}) from the paper~\cite{McKilliam_leastsqPSKpilotsdata_2012}.  This document is not self contained.  It is intended that the reader start at~\cite{McKilliam_leastsqPSKpilotsdata_2012} and refer to this document when prompted in~\cite{McKilliam_leastsqPSKpilotsdata_2012}.  The equation reference numbers in this document start at (\arabic{lasteqplusone}).  All equation numbers less than (\arabic{lasteqplusone}) refer back to~\cite{McKilliam_leastsqPSKpilotsdata_2012}.  The section numbers in this document start at~\arabic{lastsecplusone} and all sections before~\arabic{lastsecplusone} are contained in~\cite{McKilliam_leastsqPSKpilotsdata_2012}.  This document is separated into 3 sections.  Section~\ref{sec:proof-almost-sureappendix} contains those lemmas required for the proof of almost sure convergence (Theorem~\ref{thm:consistency}).  Section~\ref{sec:proof-asympt-normappendix} contains those lemmas required for the proof of asymptotic normality (Theorem~\ref{thm:normality}).  Section~\ref{sec:an-empirical-process} contains proofs for lemmas that arise in Section~\ref{sec:proof-asympt-normappendix}.  These involve the proof of~\emph{tightness} for certain empirical processes~\cite{Billingsley1999_convergence_of_probability_measures,Dudley_unif_central_lim_th_1999,Shorak_emp_proc_stat_2009}.

@@

\begin{lemma}\label{lem:chaining2}
There exists a positive constant $K_1$ such that
\[
\expect_{R,\Phi} \sup_{\sabs{\lambda} < \epsilon} \abs{ X(\lambda) } \leq K_1 \sqrt{C_\epsilon}.
\]
where $C_\epsilon$ is defined in~\eqref{eq:Cepsdefn}
\end{lemma}
\begin{IEEEproof}
Let $B_\epsilon = \{x \in \reals \mid \abs{x} < \epsilon\}$ be the set of real numbers with magnitude less than $\epsilon$.  For each non negative integer $k$, let $T_\epsilon(k)$ be a discrete subset of $B_\epsilon$ with the property that for every $\lambda \in B_\epsilon$ there exists $\lambda_1$ and $\lambda_2$ in $T_\epsilon(k)$ such that the psuedometric
\[
d_1(\lambda, \lambda_1) = \sum_{i \in P \cup D} \big( f_{i}(\lambda) - f_{i}(\lambda_1) \big)^2 \leq 2^{-k} C_\epsilon L,
\]
and the psuedometric
\[
d_2(\lambda, \lambda_2) = \sum_{i \in P \cup D} \sabs{f_{i}(\lambda) - f_{i}(\lambda_2)} \leq 2^{-k} D_\epsilon L
\]
where 
\begin{equation}\label{eq:Depsdefn}
D_\epsilon = \frac{1}{L}\epsilon\sum_{i\in P \cup D}R_i + \frac{2}{L}\sum_{i\in P \cup D}R_i I_{\epsilon}(\Phi_i).
\end{equation}
We specifically define $T_\epsilon(0)$ to contain only zero.  Defined this way, $T_\epsilon(0)$ satisfies the inequality above because $d_1(\lambda, 0) \leq C_\epsilon L $ and $d_2(\lambda, 0) \leq D_\epsilon L$ for all $\lambda \in B_\epsilon$, as a result of Lemma~\ref{lem:epslmlemma}.  
The existance of $T_\epsilon(k)$ for every positive integer $k$ will be proved by construction in Lemma~\ref{lem:metricentropy}.  Lemma~\ref{lem:metricentropy} also shows that the number of elements in $T_\epsilon(k)$ is no more that $K_3 2^k$ where $K_3$ is a constant, independent of $L$, $\epsilon$ and $k$.

@@

\begin{lemma}\label{lem:epslmlemma}
Both $d_1(\lambda, 0) \leq C_\epsilon L $ and $d_2(\lambda, 0) \leq D_\epsilon L$ for all $\lambda \in B_\epsilon$.
\end{lemma}
\begin{IEEEproof}
We prove the lemma for $d_2$.  The proof for $d_1$ is similar.  Observe that $d_2(\lambda, 0) = c_1 + c_2$ where 
 \[
 c_1 = \sum_{i \in P} R_i\sabs{\sin(\lambda + \Phi_i) - \sin(\Phi_i) }
 \]
 and 
 \[
 c_2 = \sum_{i \in D} R_i \sabs{\sin\fracpart{\lambda + \Phi_i} - \sin\fracpart{\Phi_i}}.
 \]
 As $\sin(\cdot)$ is Lipshitz continuous with constant $K=1$,
 \[
 \sabs{\sin(\lambda + \Phi_i) - \sin(\Phi_i)} \leq K\sabs{\lambda} = \sabs{\lambda} < \epsilon
 \]
 for all $i \in P \cup D$, and therefore $c_1 \leq \epsilon \sum_{i \in P} R_i$.  Let $S = \{ i \in D \mid I_\epsilon(\Phi_i) = 1\}$. Now $c_2 = c_3 + c_4$ where 
 \[
 c_3 = \sum_{i \in D, i \in S} R_i \sabs{\sin\fracpart{\lambda + \Phi_i} - \sin\fracpart{\Phi_i}}
 \]
 and
 \[
 c_4 =  \sum_{i \in D, i \notin S} R_i \sabs{\sin\fracpart{\lambda + \Phi_i} - \sin\fracpart{\Phi_i}}.
 \]
 If $i \notin S$ then $\round{\lambda + \Phi_i} = \round{\Phi_i}$ for all $\sabs{\lambda} < \epsilon$ and therefore
 \begin{align*}
 \vert\sin&\fracpart{\lambda + \Phi_i} - \sin\fracpart{\Phi_i}\vert \\
 &= \sabs{\sin(\lambda + \Phi_i - \round{\Phi_i}) - \sin(\Phi_i - \round{\Phi_i})} \\
 &\leq \sabs{\lambda} < \epsilon
 \end{align*}
and so, 
\[
c_4 \leq \epsilon \sum_{i \in D, i \notin S} R_i \leq \epsilon \sum_{i \in D} R_i.
\]
Otherwise, if $i \in S$, then $\sabs{\sin\fracpart{\lambda + \Phi_i} - \sin\fracpart{\Phi_i}} \leq 2$ because $\sin(\cdot) \leq 1$.  Thus 
\[
c_3 \leq 2 \sum_{i \in D, i \in S} R_i \leq 2 \sum_{i \in D} R_i I_\epsilon(\Phi_i).
\]
Now,
\begin{align*}
d_2(\lambda, 0) &= c_1 + c_2 \\
&\leq c_1 + c_3 + c_4 \\
&\leq \epsilon \sum_{i \in P \cup D} R_i + 2 \sum_{i \in D} R_i I_\epsilon(\Phi_i) \\
&= D_\epsilon L
\end{align*}
as required
\end{IEEEproof}

\begin{lemma}\label{lem:limexpTk} With $T_\epsilon(k)$ defined as in Lemma~\ref{lem:chaining2},
\[
\lim_{k\rightarrow\infty}\expect_{R,\Phi}\sup_{\lambda \in T_\epsilon(k)} \sabs{X(\lambda)} = \expect_{R,\Phi} \sup_{\sabs{\lambda} < \epsilon} \sabs{X(\lambda)}
\]
\end{lemma}
\begin{IEEEproof}
Let $b_2(\lambda)$ be a function that maps $\lambda \in B_\epsilon$ to a point in $T_\epsilon(k)$ such that  $d_2(\lambda,b_2(\lambda)) \leq 2^{-k}D_\epsilon L$.  The existance of $b_2$ is guaranteed by the definition of $T_\epsilon(k-1)$.  So, for all $\lambda \in B_\epsilon$,
\begin{align*}
\sabs{X(\lambda) - X(b_2(\lambda))} &= \abs{\frac{1}{\sqrt{L}}\sum_{i\in P \cup D}g_i(f_i(\lambda) - f_i(b_2(\lambda)))} \\
&\leq  \frac{1}{\sqrt{L}}\sum_{i\in P \cup D}\abs{g_i}\sabs{f_i(\lambda) - f_i(b_2(\lambda))} \\
&\leq \frac{1}{\sqrt{L}} \sum_{i\in P \cup D} g_\text{max} \sabs{f_i(\lambda) - f_i(b_2(\lambda))} \\
&\leq \frac{g_\text{max}}{\sqrt{L}} d_2(\lambda,b_2(\lambda)) \\
&\leq \frac{g_\text{max}}{\sqrt{L}} 2^{-k} D_\epsilon L,
\end{align*}
where $g_\text{max} = \sup_{i\in P\cup D} \abs{g_i}$. The bound applies uniformly over $\lambda \in B_\epsilon$, so
\[
\sup_{\sabs{\lambda} < \epsilon} \sabs{X(\lambda) - X(b_2(\lambda))} \leq \frac{g_\text{max}}{\sqrt{L}} 2^{-k} D_\epsilon L.
\]
Applying $\expect_{R,\Phi}$ to both sides,
\[
\expect_{R,\Phi} \sup_{\sabs{\lambda} < \epsilon} \sabs{X(\lambda) - X(b_2(\lambda))} \leq K_4 2^{-k} D_\epsilon L,
\]
where, as a result of Lemma~\ref{lem:maxineq},
\[
K_4 = \tfrac{1}{\sqrt{L}}\expect_{R,\Phi} g_\text{max} \leq 3 \sqrt{\frac{\log L}{L}}
\]
is independent of $\epsilon$ and $k$.  Because $T_\epsilon(k)$ is a subset of $B_\epsilon$,
\[
\sup_{\lambda \in T_\epsilon(k)} \expect_{R,\Phi} \sabs{X(\lambda)} \leq \sup_{\sabs{\lambda} < \epsilon} \expect_{R,\Phi} \sabs{X(\lambda)},
\]
and so,
\begin{align*}
0 &\leq \sup_{\sabs{\lambda} < \epsilon} \expect_{R,\Phi} \sabs{X(\lambda)} - \sup_{\lambda \in T_\epsilon(k)} \expect_{R,\Phi} \sabs{X(\lambda)} \nonumber \\
&\leq \sup_{\sabs{\lambda} < \epsilon} \expect_{R,\Phi} \sabs{X(\lambda)} - \sup_{\sabs{\lambda} < \epsilon} \expect_{R,\Phi} \sabs{X(b_2(\lambda))} \nonumber \\
&\leq \sup_{\sabs{\lambda} < \epsilon} \expect_{R,\Phi} \big( \sabs{X(\lambda)} - \sabs{X(b_2(\lambda))} \big) \nonumber \\
&\leq \sup_{\sabs{\lambda} < \epsilon} \expect_{R,\Phi} \sabs{X(\lambda) - X(b_2(\lambda))} \nonumber \\
&\leq K_4 2^{-k} D_\epsilon L. \label{eq:Deps2nktozero}
\end{align*}
The second line in the inequaliy above follows because,
\[
\sup_{\sabs{\lambda} < \epsilon} \expect_{R,\Phi} \sabs{X(b_2(\lambda))} \leq \sup_{\lambda \in T_\epsilon(k)} \expect_{R,\Phi} \sabs{X(\lambda)},
\]
since $b_2(\lambda) \in T_\epsilon(k)$.  The lemma follows because $K_4 2^{-k} D_\epsilon L$ goes to zero as $k\rightarrow\infty$.
\end{IEEEproof}

@@

\begin{lemma}\label{lem:chaining3}(Chaining)
For all positive integers $k$,
\[
\expect_{R,\Phi} \sup_{\lambda \in T_\epsilon(k) } \abs{ X(\lambda) } \leq \sqrt{C_\epsilon} \sum_{i=1}^k \frac{5\sqrt{i \log 2 + \log K_3}}{2^{i/2}}.
\]
\end{lemma}
\begin{IEEEproof}
Let $b_1(\lambda)$ map each $\lambda \in T_\epsilon(k)$ to an element in $T_\epsilon(k-1)$ such that $d(\lambda, b_1(\lambda)) \leq 2^{1-k}C_\epsilon L$.  The existance of $b_1$ is guaranteed by the definition of $T_\epsilon(k)$.  By the triangle inequality
\[
\sabs{X(\lambda)} \leq \sabs{X(b_2(\lambda))} + \sabs{X(\lambda) - X(b_2(\lambda))}  
\]
and taking supremums on both sides,
\begin{align}
&\sup_{\lambda \in T_\epsilon(k)}\sabs{X(\lambda)} \nonumber \\
&\leq \sup_{\lambda \in T_\epsilon(k)}\sabs{X(b_2(\lambda))} + \sup_{\lambda \in T_\epsilon(k)} \sabs{X(\lambda) - X(b_2(\lambda))}   \nonumber \\
&\leq \sup_{\lambda \in T_\epsilon(k-1)}\sabs{X(\lambda)} + \sup_{\lambda \in T_\epsilon(k)} \sabs{X(\lambda) - X(b_2(\lambda))}, \label{eq:Xb2recpreexp}
\end{align}
the last line because $b_2(\lambda) \in T_\epsilon(k-1)$ and so
\[
\sup_{\lambda \in T_\epsilon(k)}\sabs{X(b_2(\lambda))} \leq \sup_{\lambda \in T_\epsilon(k-1)}\sabs{X(\lambda)}.
\]
Conditional on $\{R_i\}$ and $\{\Phi_i\}$ the random variable
\[
U(\lambda) = X(\lambda) - X(b_2(\lambda))
\]
has zero mean and is normally distributed with variance
\begin{align*}
\sigma_U^2 &= \expect_{R,\Phi} \frac{1}{L} \sum_{i \in P \cup D} g_i^2 \big( f_i(\lambda) - f_i(b_2(\lambda)) \big)^2 \\
&=  \frac{1}{L} \sum_{i \in P \cup D} \big( f_i(\lambda) - f_i(b_2(\lambda)) \big)^2 \\
&= d(\lambda, b_2(\lambda)) \leq 2^{1-k} C_\epsilon,
\end{align*}
since $\expect_{R,\Phi}g_i^2 = 1$.  So, from Lemma~\ref{lem:maxineq},
\begin{align*}
\expect_{R,\Phi} \sup_{\lambda \in T_\epsilon(k)} \sabs{U(\lambda)} &\leq 3 \sqrt{ 2^{1-k} C_\epsilon \log \abs{T_\epsilon(k)} } \\
&\leq \sqrt{C_\epsilon} \frac{5\sqrt{k \log 2 + \log K_3}}{2^{k/2}}.
\end{align*}
Taking expectations on both sides of~\eqref{eq:Xb2recpreexp},
\begin{align*}
\expect_{R,\Phi}&\sup_{\lambda \in T_\epsilon(k)}\sabs{X(\lambda)} \\
&\leq \expect_{R,\Phi}\sup_{\lambda \in T_\epsilon(k-1)}\sabs{X(\lambda)} + \sqrt{C_\epsilon} \frac{5\sqrt{k \log 2 + \log K_3}}{2^{k/2}} ,
\end{align*}
which involves a recursion in $k$.  By unravelling the recursion and using that $T_\epsilon(k)$ contains only zero, and therefore
\[
\expect_{R,\Phi} \sup_{\lambda \in T_k(0)} \sabs{X(\lambda)} = \expect_{R,\Phi} \sabs{X(0)} = 0
\]
we obtain,
\[
\expect_{R,\Phi}\sup_{\lambda \in T_\epsilon(k)}\sabs{X(\lambda)} \leq  \sqrt{C_\epsilon} \sum_{i=1}^k \frac{5\sqrt{i \log 2 + \log K_3}}{2^{i/2}}  
\]
as required.
\end{IEEEproof}

\begin{lemma}\label{lem:maxineq}(Maximal inequalities)
Suppose $X_1, \dots, X_N$ are zero mean Gaussian random variables each with variance less than some positive constant $K$.  Then
\[
\expect \sup_{n = 1, \dots, N} \abs{X_n} \leq 3  \sqrt{K \log N}
\]
where $\log N$ is the natural logarithm of $N$.
\end{lemma}
\begin{IEEEproof}
This result is well known, see for example~\cite[Section 3]{Pollard_asymp_empi_proc_1989}  
\end{IEEEproof}
